My title

### 2024-03-11 paper/paper.qmd
new update to paperrrrr

toronto_shelters_clean |>
  ggplot(aes(x = occupancy_rate_rooms, y = capacity_actual_room)) +
  geom_point(alpha = 0.1) +
  theme_classic()
```

>>>>

ggplot(toronto_shelters_clean, aes(x = occupancy_rate_rooms, y = capacity_actual_room)) +
  geom_point(alpha = 0.2, color = "blue") + 
  geom_smooth(method = "lm", se = FALSE, color = "red") +  theme_minimal() + labs(title = "Analysis of Shelter Capacity vs. Occupancy Rate",
    x = "Occupancy Rate of Rooms",
    y = "Actual Room Capacity"
  )
```
